### 2021-05-15 geography/ia/paper.tex
added ecole militaire picture
geo ia work, refactoring, math ia fixes

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\linewidth]{arrts.png}
    \caption{A map of Paris \textit{arrondissements}, drawn by hand.}
\end{figure}

@@

    \item As there are more people moving about in residential areas, for example in cars for the morning commute or at noon for lunch, it can logically be theorized that noise pollution, which is obviously a function of the amount of people, would be higher in these places. Today it is estimated that an average noise level of $60dB$ can be found in residential areas, according to the comprehensive Bruitparif government-sponsored report. \footcite{bruitparif} This value largely surpasses the WHO's safe level of $53dB$. \footcite{who_noise_guidelines}

@@

\begin{figure}[h!]
    \begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=0.7\linewidth]{no2_map.png}
    \caption{A map of Paris NO2 levels in 2018, as reported by AirParif, on the official Paris website \protect\footcite{paris_air_qual}}
    \end{minipage}
\end{figure}

@@

We chose 10 sites in total to study, shown below in Figures 3, 4.

\begin{figure}[H]
    \begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=0.7\linewidth]{no2_map.png}
    \caption{Map of sites chosen for the residential area, the XVI\textsuperscript{th} \textit{arrondissement}. Map base layer courtesy of Google Maps, pictures seen are taken on a mobile phone.}
    \end{minipage}
\end{figure}

\begin{figure}[H]
    \begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=0.7\linewidth]{no2_map.png}
    \caption{Map of sites chosen for the residential area, the XVI\textsuperscript{th} \textit{arrondissement}. Map base layer courtesy of Google Maps, pictures seen are taken on a mobile phone.}
    \end{minipage}
\end{figure}

\subsection{Sampling choices}

The method we will be using to select the sites from where we will take the Bipolar survey is Stratified which means that we are choosing the sites ourselves. The reason we chose this is to make sure that we got a good variety of sites that would give a good idea of the general environmental quality of that area, but also to avoid the selection of residential areas, which do in fact exist in the VIIe, which would happen if we chose the random sampling method. This stratified sampling approach would best represent the targeted area and yield meaningful data on tourist-heavy sites.

The sampling method we used to select our sites is the stratified method. The reason for this choice is that we get a

@@

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\linewidth]{media/arrts.png}
    \caption{A map of Paris \textit{arrondissements}, drawn by hand.}
\end{figure}

@@

    \item As there are more people moving about in residential areas, for example in cars for the morning commute or at noon for lunch, it can logically be theorized that noise pollution, which is obviously a function of the amount of people, would be higher in these places. Today it is estimated that an average noise level of $60dB$ can be found in residential areas, according to the very comprehensive Bruitparif government-sponsored report. \footcite{bruitparif} This value largely surpasses the WHO's safe level of $53dB$. \footcite{who_noise_guidelines}

@@

\begin{figure}[h!]
    \begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=0.7\linewidth]{media/no2_map.png}
    \caption{A map of Paris NO2 levels in 2018, as reported by AirParif, on the official Paris website \protect\footcite{paris_air_qual}}
    \end{minipage}
\end{figure}

% NEW SECTION

@@

We chose 10 sites in total to conduct a bipolar survey, shown below in Figures 3, 4.

\begin{figure}[H]
    \begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=0.7\linewidth]{media/16esites.png}
    \caption{Map of sites chosen for the residential area, the XVI\textsuperscript{th} \textit{arrondissement}. Map base layer courtesy of Google Maps, pictures seen are taken on a mobile phone.}
    \end{minipage}
\end{figure}

This site was chosen as, like stated before, it is a residential area. There are other residential areas, however this one was specifically chosen for reasons of convenience.

\begin{figure}[H]
    \begin{minipage}{\textwidth}
    \centering
    \includegraphics[width=0.7\linewidth]{media/7esites.png}
    \caption{Map of sites chosen for the residential area, the XVI\textsuperscript{th} \textit{arrondissement}. Map base layer courtesy of Google Maps, pictures seen are taken on a mobile phone.}
    \end{minipage}
\end{figure}

This area in the VII\textsuperscript{th} was chosen as it is a staple of tourism in France. It is home to the famed Eiffel Tower, the Ecole Militaire building and the Seine river bank.

\subsection{Our sampling method}

The sites in the two areas were chosen using a method of stratified sampling, as seeing that the VVI\textsuperscript{th} does indeed contain residential sites and the XVI\textsuperscript{th} touristic ones, we can discard the ones that are irrelevant to our study.

\subsection{Method}

\subsubsection{Bipolar semantic survey}

The sites will be visited to conduct a so-called "bipolar survey", which consists of rating the site based on multiple criteria. This process was done by selecting a single person from our group to visit one of the sites, and complete a bipolar semantic survey. They would grade several different aspects of the site (such as general cleanliness, noise, amount of cars), and take a set of 3 images of the site.\footnote{Images taken for our study can be found at \url{https://github.com/kinnounko/notes/tree/main/geography/ia/images}}

\subsubsection{Statistical evaluations}

In order to either support or disprove our third hypothesis, it is important to study how trees are scattered in Paris, which reveals how dispersed green spaces are from one another. A statistical test called the Nearest Neighbor Index (NNI) test can provide a reasonable answer to this: if the index is similar for both sites, it can easily be said then that our hypothesis is supported. This value also reveals information about the distribution of trees: clustered, random or in a regular pattern, as seen in Figure 5 below.

\begin{figure}[H]
    \centering
    \includegraphics[width=0.2\linewidth]{media/nni1.png}
    \includegraphics[width=0.2\linewidth]{media/nni2.png}
    \includegraphics[width=0.2\linewidth]{media/nni3.png}
    \caption{The NNI measures the spacial distribution of data. From a value of 0, representing a clustered pattern, to 1 (random) and to 2.15 (uniform pattern)}
\end{figure}

As individually counting trees in these areas would be a tedious task, we used the Paris OpenData platform (licensed under the permissive ODbL license\footcite{odbl}), owned by the government. The fact that this kind of database platform exists, shows a certain level of transparency on the government's part.

We used the trees dataset procured from this library, which contains the exact coordinates of trees in the city. \footcite{paris_opendata} There are also other information such as species of the tree and such, however these are cleaned from the dataset for our purposes.

A script, written in Python was programmed for the task of calculating the NNI value, because with a dataset of over 20,000 data points this would not be possible by hand. We go through each point, and find its nearest neighbor. In order to calculate distances between these two points, we use the Haversine Formula, as the two points would be in the form of coordinates. With this information the NNI can be calculated with the simple formula

$$Rn = \frac{2 \bar D}{\sqrt{\frac{a}{n}}}$$

where $Rn$ is the NNI index value, $\bar D$ is the mean observed distance to the nearest neighbor, $a$ is the area of the zone and $n$ is the total number of data points.

% NEW SECTION

@@

All media and information related to this IA can be found on the URL \url{https://github.com/kinnounko/notes/tree/main/geography/ia}. This includes images, the \LaTeX{} source code to this paper, and the Python program used to calculate the NNI value.

### 2021-05-15 math/ia_2021/paper.tex
geo ia
geo ia work, refactoring, math ia fixes

\subsection{Processing the dataset for use}
%TODO: #2 Ask for help 
The dataset, procured from the National Oceanic and Atmospheric Administration website \cite{noaa}, includes many tsunami
runups, going back before the year 0. Due to this, the NOAA states uncertainties
that can occur in its data. For example, reports that were recorded before the
20th century tend to be based on written accounts, and not recorded seismic activity.
Only since the 1960s, the installation of the Worldwide Standardized Seismograph
Network system allowed for more accurate data in this paper. For that reason, any recorded
activity before this date was discarded from the dataset for this paper. The dataset itself can
be accessed through two different methods; searching the database using the online
tool or downloading it in a somewhat obscure compressed Google Earth \verb|.kmz| format.
The online tool supports the download of search results in a much more human-readable
\verb|.tsv| (tab-separated) format. For this paper, all entries after the year 1900 were searched and downloaded.

@@

$SS_{res} = \sum\limits_{i} e_i^2 = \sum\limits_{i} (y_i - p_i)^2$, \footnote{$\sum\limits_{i=1}^n x_i$ means that all values of x are summed, beginning from $x_1$ and ending at $x_n$} where $e_i$ is the error term, equal to the difference of a data point $y_i$ and its corresponding predicted value $p_i$.

@@

When attempting to predict the maximum wave height of a tsunami such as the one caused by the 2011 earthquake off the Pacific coast of Tōhoku, approximately 70km away from shore, which produced a 38.9m wave \cite{yomiuri_2011}. The model in this paper approximates this same event as only a 8m wave, when supplied the 9.0 magnitude of the earthquake and the 70km distance. These types of errors can be attributed to the fact that there are many more independent variables, such as the shape of the seafloor for example, that can amplify or potentially change the height of a tsunami's wave.

>>>>

\subsection{Processing the dataset for use}

The dataset, procured from the National Oceanic and Atmospheric Administration website \cite{noaa}, includes many tsunami runups, going back before the year 0. Due to this, the NOAA states uncertainties that can occur in its data. For example, reports that were recorded before the 20th century tend to be based on written accounts, and not recorded seismic activity. Only since the 1960s, the installation of the Worldwide Standardized Seismograph Network system allowed for more accurate data in this paper. For that reason, any recorded activity before this date was discarded from the dataset for this paper. The dataset itself can be accessed through two different methods; searching the database using the online tool or downloading it in a somewhat obscure compressed Google Earth \verb|.kmz| format. The online tool supports the download of search results in a much more human-readable \verb|.tsv| (tab-separated) format. For this paper, all entries after the year 1900 were searched and downloaded.

@@

$SS_{res} = \sum\limits_{i} e_i^2 = \sum\limits_{i} (y_i - p_i)^2$, \footnote{$\sum\limits_{i=1}^n x_i$ means that all values of $x$ are summed, beginning from $x_1$ and ending at $x_n$} where $e_i$ is the error term, equal to the difference between a data point $y_i$ and its corresponding predicted value $p_i$.

@@

When attempting to predict the maximum wave height of a tsunami such as the one caused by the 2011 earthquake off the Pacific coast of Tōhoku, Japan, approximately 70km away from shore, which produced a 38.9m wave \cite{yomiuri_2011}. The model in this paper approximates this same event as only a 8m wave, when supplied the 9.0 magnitude of the earthquake and the 70km distance. These types of errors can be attributed to the fact that there are many more independent variables, such as the shape of the seafloor for example, that can amplify or potentially change the height of a tsunami's wave.

It has also come to my attention that using the $R^2$ value for a non-linear relationship is not suitable, as it does not follow the same characteristics.
